On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-07-10 manuscripts/PNAS/chazthm_pnas.tex
newness

Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that imply stable sparse representations.  Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$,
we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$. We also say $E$ is \emph{regular} when every element of $[m]$ is contained in exactly $\ell$ elements of $E$ for some $\ell > 0$ (for given $\ell$, we say $E$ is \textit{$\ell$-regular}).

@@

Next, we describe a quantitative version of the spark condition.  
The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}. By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound. This motivates the following definition: 
%\begin{align*}
%L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
%\end{align*}
\begin{align*}
L_E(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in E \right\}
%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
\end{align*} 
%
and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: note that $L_2$ implied by $L_E$]

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix a matrix $\mathbf{A} \in \mathbb{R}^{n \times m}$ with $L_E(\mathbf{A}) > 0$ for some regular $E \subseteq {[m] \choose k}$ with the SIP. If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$, an associated permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|(\mathbf{A_J})_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
\end{align}
%
for some non-empty $J, \bar J \subseteq [m]$ of size $\bar m - r(\bar m - m)$.

@@

%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}. Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $E$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}. For example, if $E$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$. The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$. When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, consecutive intervals of length $k$ in some cyclic order on $[m]$.
In fact, even if $E$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ may give the indices $J \subseteq [m]$. For sake of brevity, we delay to the next section a clear statement of this more general result.

@@

As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumptions of regularity and SIP on the hypergraph $E \subseteq {[m] \choose k}$. If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $E$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
\begin{align}\label{pcond}
\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
\end{align}
Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$. For the benefit of the reader, we do not prove this more general result below; it can be gleaned by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $E$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:

@@

We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming without loss of generality that $\bar m = m$. First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_E$ implies the following frequently applied inequality valid for any $E \subseteq 2^{[m]}$:
\begin{align}\label{delrho}
L_{E}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2,
\end{align}
For $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}. Thus, 
\begin{align*}
\|\mathbf{BPD}\mathbf{x}\|_2 
&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2.
\end{align*}

@@

If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$ we have:
\begin{align}\label{GapUpperBound}
d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \  \text{for $S \in E$},
\end{align}
then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{MainLemmaBPD}
\|(\mathbf{A}_J)_j - \mathbf{BPD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
\end{align}
for some non-empty $J$ of size $\bar m - r(\bar m - m)$.
\end{lemma}

@@

\section{Discussion}\label{Discussion}
[ TODO ]
%[mention dictionary size independence]
%In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity. Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}. We also collect a set of useful mathematical tools and basic facts for future research. The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies. We elaborate on these applications below after discussing theoretical aspects.

%What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm. This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement. In other words, a small perturbation of the data should result in only slightly different inferred parameters. In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters. Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise. It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results. We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants will improve as well.

%One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary. Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future. For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.

%A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}. Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee. For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.

%In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations. For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}. Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}). In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.

%In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons. Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}. Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).

@@

If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} (|\pi(S)| -|S|) \geq 0$ and:
\begin{align}\label{cond}
|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq E,
\end{align}
then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some $J \subseteq [m]$ of size $p \geq 1$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$. In particular, if $E$ is $d$-regular then $p = \bar m - d(\bar m - m)$. 
\end{lemma}

>>>>

Before stating our main results, we first identify combinatorial criteria on the support sets of generating codes that imply stable sparse representations.  Letting $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$, we say a hypergraph $E \subseteq 2^{[m]}$ on vertices $[m]$ is \textit{$k$-uniform} when in fact $E \subseteq {[m] \choose k}$. The \emph{degree} $\deg(i)$ of a node $i \in [m]$ is the number of elements in $E$ which contain $i$, and we say $E$ is \emph{regular} when for some $r$ we have $\deg(i) = r$ for all $i$ (for given $r$, we say $E$ is \textit{$r$-regular}).

@@

Next, we describe a quantitative version of the spark condition.  
The \emph{lower bound} $L$ of a matrix $\mathbf{M} \in \mathbb R^{n \times m}$ is the largest number $\alpha$ such that \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}. By compactness of the unit sphere, every injective linear map has a nonzero lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then each submatrix formed from $2k$ of its columns or less has a nonzero lower bound. This motivates the following definition: 
%\begin{align*}
%L_k(\mathbf{M}) := \frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
%\end{align*}
\begin{align*}
L_E(\mathbf{M}) := \inf \left\{ \frac{ \|\mathbf{M}_{S \cup S'}\mathbf{x}\|_2 }{ \sqrt{2k} \|\mathbf{x}\|_2} : \mathbf{x} \in \mathbb{R}^{|S\cup S'|}, \ \ S,S' \in E \right\}
%\frac{1}{\sqrt{k}}\max \{ \alpha : \|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2 \text{ for all $k$-sparse } \mathbf{x}\}.
\end{align*} 
%
and we write $L_{2k}:= L_E$ when $E = {[m] \choose k}$. Note that $ L = L_{\{[m]\}}$ whereas $L_{[m]} = L_2$. [TODO: Note when $L_2 > 0$ is implied by $L_E > 0$.]

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix a real $n \times m$ matrix $\mathbf{A}$ with $L_E(\mathbf{A}) > 0$ for some $r$-regular $E \subseteq {[m] \choose k}$ with the SIP. If the sequence \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} contains, for each $S \in E$, more than $(k-1){m \choose k}$ $k$-sparse vectors in general linear position supported on $S$, then there is a constant\footnote{We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).} $C_1 > 0$ for which the following holds for all $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

Every real $n \times \bar m$ matrix $\mathbf{B}$ for which there exist $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon$} for all $i$ has $\bar m \geq m$ and, provided $\bar m < mr/(r-1)$,
\begin{align}\label{Cstable}
\|(\mathbf{A_J})_j- \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J,
\end{align}
%
for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$, permutation $\mathbf{P}$ and invertible diagonal $\mathbf{D}$.

@@

%In fact, a more general result (stated clearly in the next section) can be gleaned from our method of proving Thm.~\ref{DeterministicUniquenessTheorem}. Briefly, in cases where $\mathbf{B}$ has $\bar m \neq m$ columns, or $E$ is not regular or only partially satisfying the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ gives indices $J \subseteq [m]$ defining a submatrix $\mathbf{A}_J$ and subvectors $\mathbf{x}_i^J$ that are recoverable in the sense of \eqref{Cstable} and \eqref{b-PDa}. For example, if $E$ is $\ell$-regular with the SIP but $m \leq \bar m < m\ell/(\ell - 1)$ then we have nonzero $|J| = \bar m - \ell(\bar m - m)$. The implication here is that the smaller the difference $\bar m - m$, the more columns and code entries of the original $n \times m$ dictionary $\mathbf{A}$ and codes $\mathbf{x}_i$ contained (up to noise) in the appropriately scaled $n \times \bar m$ dictionary $\mathbf{B}$ and codes $\mathbf{\bar x}_i$. When $\bar m = m$, we recover Thm.~\ref{DeterministicUniquenessTheorem}.
Regarding the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}, it is easy to verify that for every $k < m$, there is a regular $k$-uniform hypergraph that satisfies the SIP; for instance, take the consecutive intervals of length $k$ in some cyclic order on $[m]$.
In fact, even if $E$ is not regular or only partially satisfies the SIP, a relation between $\bar m$ and the degree sequence of nodes in $E$ may give the indices $J \subseteq [m]$. For sake of brevity, we delay to the next section a clear statement of this more general result.

@@

As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result that forgoes the assumption that $E \subseteq {[m] \choose k}$ is regular and satisfies the SIP. If instead we require only that the stars $\cap H(i)$ intersect at singletons for all $i \leq q$ (assuming that the nodes of $E$ are labeled in some order of non-increasing degree), we have that $\bar m \geq k|E| / \deg(1)$ and, provided $\bar m < k|E| / (\deg(1) - 1)$, the non-empty submatrix $J$ is of size equal to the largest number $p$ satisfying:
\begin{align}\label{pcond}
\sum_{i=\ell}^{m} \deg(i) > (\bar m + 1 - \ell) (\deg(\ell) - 1) \ \ \text{for all } \ell \leq p \leq q.
\end{align}
Specifically, $J$ consists of the union of the set of all nodes of degree exceeding $\deg(p)$ and some subset of those nodes with degrees equal to $\deg(p)$. For the benefit of the reader, we do not prove this more general result below; it can be gleaned by examining how exactly Lemma \ref{NonEmptyLemma} is incorporated into the proof of Lem.~\ref{MainLemma}.
%As mentioned in the previous section, Thm.~\ref{DeterministicUniquenessTheorem} is a particular case of a more general result, which requires a looser set of constraints on the hypergraph $E$ and which applies to $n \times \bar m$ matrices $\mathbf{B}$ (and $\bar m$-dimensional codes $\mathbf{\bar x}_i$) with $\bar m \neq m$:

@@

We now begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $L_{2k}(\mathbf{A}) > 0$ and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, temporarily assuming (without loss of generality) that $\bar m = m$. First, note that $\|\mathbf{x}\|_1 \leq \sqrt{k} \|\mathbf{x}\|_2$ for $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, which by definition of $L_{2k}$ implies the following frequently applied inequality:
\begin{align}\label{delrho}
L_{2k}(\mathbf{A}) \leq \frac{\|\mathbf{A}\mathbf{x}\|_2}{\sqrt{2k} \|\mathbf{x}\|_2} 
\leq  \max_{j \in [m]}\|\mathbf{A}_j\|_2.
\end{align}
For $k$-sparse $\mathbf{x} \in \mathbb{R}^m$, the triangle inequality gives \mbox{$\|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2  \leq C_1\varepsilon \|\mathbf{x}\|_1 \leq C_1 \varepsilon \sqrt{2k}  \|\mathbf{x}\|_2$}. Thus, 
\begin{align*}
\|\mathbf{BPD}\mathbf{x}\|_2 
&\geq | \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A}-\mathbf{BPD})\mathbf{x}\|_2 | \\
&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2.
\end{align*}

@@

If for some  $\mathbf{B} \in \mathbb{R}^{n \times \bar m}$ and map $\pi: E \mapsto {[\bar m] \choose k}$ we have:
\begin{align}\label{GapUpperBound}
d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon, \ \  \text{for $S \in E$},
\end{align}
then $\bar m \geq m$, and provided $\bar m < mr /(r-1)$, there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{MainLemmaBPD}
\|(\mathbf{A}_J)_j - \mathbf{B}_{\bar J} \mathbf{PD}_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
\end{align}
for some non-empty $J, \bar J$ of size $\bar m - r(\bar m - m)$.
\end{lemma}

@@

\section{Discussion}\label{Discussion}
[ TODO ]
%[mention dictionary size independence]
In this note, we generalized the approach of \cite{Hillar15} to prove the stability of unique solutions to Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} while significantly reducing the known sample complexity. Our results justify the application of the sparse linear coding model to blind source separation problems, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements, \eqref{LinearModel}. We also collect a set of useful mathematical tools and basic facts for future research. The main motivation for this work, however, was to understand how seemingly universal representations emerge from sparse coding models fit to natural data by a variety of methodologies. We elaborate on these applications below after discussing theoretical aspects.

What we have shown here is that the sparse linear coding model generally produces a \textit{well-posed} inverse problem to be approximately solved by a numerical algorithm. This early concept of Hadamard \cite{Hadamard1902} can be paraphrased as the idea that inferences from observations should be robust to the inevitable uncertainty in measurement. In other words, a small perturbation of the data should result in only slightly different inferred parameters. In this regard, for the sparse linear coding model we demonstrate a linear relationship, \eqref{epsdel}, between measurement noise and the deviation of any solution from the true parameters, with explicit constants expressed in terms of these parameters. Moreover, we show that even if the meta-parameter for the number of dictionary elements is overestimated, a subset of parameters may still be identifiable up to noise. It would therefore be of practical utility to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ in Def.\ref{maindef} as well as the minimal requirements on the number and diversity of generating codes, and we hope that other researchers continue to improve and extend our results. We remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be smaller when sampled from a distribution; in such cases, the constants will improve as well.

One notable component of our contribution is a combinatorial criteria (regular hypergraphs satisfying the singleton intersection property, Def.~\ref{sip}) for the support sets of sparse codes key to the identification of the dictionary. Fully understanding those combinatorial designs allowing for stable sparse representations is an interesting research area for the future. For instance, whether there is a support set size $N$ that is polynomial in $m,k$ gauranteeing the conclusions of Thm.~\ref{DeterministicUniquenessTheorem} has implications for the computational complexity of Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} and related questions \cite{Tillmann15}.

A technical difficulty in proving Thm.~\ref{DeterministicUniquenessTheorem} was the absence of a spark condition assumption on solutions to Prob.~\ref{InverseProblem}. Although mathematically interesting that no such requirement is necessary, there are other reasons to seek out such a theoretical guarantee. For instance, it is difficult to ensure that an algorithm maintain a dictionary satisfying \eqref{SparkCondition} at each iteration; indeed, even certifying a dictionary has this property is likely intractable given its NP-hardness \cite{tillmann2014computational}.

In fact, uniqueness guarantees with minimal assumptions apply to all areas of data science and engineering that utilize learned sparse representations. For example, several groups have applied compressive sensing to signal processing tasks: MRI analysis \cite{lustig2008compressed}, image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}. Given such effective uses of compressive sensing, it is only a matter of time before these systems incorporate dictionary learning to encode and process data (e.g., in a device that learns structure from motion \cite{kong2016prior}). In these cases, assurances such as those offered by our theorems certify that different devices (with different initialization, samples, etc.) will learn equivalent representations given enough data from statistically identical systems.

In the field of theoretical neuroscience in particular, dictionary learning for sparse coding and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12} that reproduce response properties of cortical neurons. Our results suggest that this correspondence could be due to the ``universality'' of sparse representations in natural data, an early mathematical idea in neural theory \cite{pitts1947}. Furthermore, they justify the hypothesis of \cite{Coulter10, Isely10} that sparse codes passed through information bottlenecks in the brain are recovered from random projections via (unsupervised) biologically plausible sparse coding (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).

@@

If the map $\pi: E \to 2^{[\bar m]}$ has $\sum_{S \in E} (|\pi(S)| -|S|) \geq 0$ and:
\begin{align}\label{cond}
|\cap \pi(F)| \leq |\cap F | \text{ for all } F \subseteq E,
\end{align}
then $\bar m \geq\sum_i \deg(i) / \deg(1)$, and if $\bar m < \sum_i \deg(i) / (\deg(1) - 1)$ then the association $i \mapsto \cap \pi(F(i))$ defines an injective map to $[\bar m]$ from some non-empty $J \subseteq [m]$ of size $p$ consisting of the union of the set of all nodes of degree exceeding $\deg(p)$ and some set of nodes all having degree equal to $\deg(p)$. In particular, if $E$ is $r$-regular then $|J| = \bar m - r(\bar m - m)$. 
\end{lemma}
